---
title: Compare characteristics of network consenting vs non-consenting participants
output: html_document
date: "2023-01-15"
editor_options: 
  markdown: 
    wrap: 72
---

```{r, setup, include=FALSE}
rm(list=ls())
library(dplyr)
```

```{r, data_loc, include=FALSE}
data_loc <- "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT/"
```


```{r}
tab2_dt <- as.data.frame(readRDS(paste0(data_loc, "tab2_comparison_data.RDS")))
class(tab2_dt)
dim(tab2_dt)
colnames(tab2_dt)
```

Compare `FUSNCONSENT == 7` vs not. 

Recode NA is FUSNCONSENT as 0 for easier comparison

'FUSNCONSENT == 7` -- consent
'FUSNCONSENT == 0` -- not consent

```{r}
tab2_dt <- 
  tab2_dt %>% mutate(FUSNCONSENT_numeric = 
                     ifelse(is.na(FUSNCONSENT), 0, FUSNCONSENT))
```

```{r}
total_fusconsent_7 = sum(tab2_dt$FUSNCONSENT_numeric == 7)
total_fusconsent_7
total_fusconsent_0 = sum(tab2_dt$FUSNCONSENT_numeric == 0)
total_fusconsent_0

t.test(as.numeric(tab2_dt$age[tab2_dt$FUSNCONSENT_numeric == 7]),
       as.numeric(tab2_dt$age[tab2_dt$FUSNCONSENT_numeric == 0])
       )


table(tab2_dt$gender_3cat)

```

```{r}
  tab2_dt %>%  
  select(gender_3cat, FUSNCONSENT_numeric) %>%
  group_by(FUSNCONSENT_numeric)

gender_xtab <- 
  xtabs(~factor(tab2_dt$gender_3cat)+factor(tab2_dt$FUSNCONSENT_numeric))

chisq.test(gender_xtab)
chisq.test(gender_xtab[1:2, 1:2])
```

Test for age
```{r}
stats_age <- tab2_dt %>%
  mutate(age_numeric = as.numeric(as.character(age))) %>%  # Convert age to numeric
  group_by(FUSNCONSENT_numeric) %>%
  summarise(
    mean_age = mean(age_numeric, na.rm = TRUE),
    sd_age = sd(age_numeric, na.rm = TRUE)
  )

print(stats_age)



```


```{r}
# Convert age to numeric
tab2_dt$age_numeric <- as.numeric(as.character(tab2_dt$age))

# Split data based on FUSNCONSENT_numeric
group1 <- tab2_dt$age_numeric[tab2_dt$FUSNCONSENT_numeric == 0]
group2 <- tab2_dt$age_numeric[tab2_dt$FUSNCONSENT_numeric == 7]

# Perform t-test
t_test_result <- t.test(group1, group2)

print(t_test_result)

```

Test for Gender

```{r}
#male_count
tab2_dt %>%
  filter(FUSNCONSENT_numeric %in% c(0, 7), gender_3cat == "1") %>%
  group_by(FUSNCONSENT_numeric) %>%
  summarise(male_count = n())

tab2_dt %>%
  filter(FUSNCONSENT_numeric %in% c(0, 7), gender_3cat == "2") %>%
  group_by(FUSNCONSENT_numeric) %>%
  summarise(female_count = n())

tab2_dt %>%
  filter(FUSNCONSENT_numeric %in% c(0, 7), gender_3cat == "3") %>%
  group_by(FUSNCONSENT_numeric) %>%
  summarise(not_reported_count = n())
```

```{r}
# Create the contingency tables for each gender category
male_xtab <- xtabs(~gender_3cat + FUSNCONSENT_numeric, data = filter(tab2_dt, gender_3cat == "1"))
print(male_xtab)
female_xtab <- xtabs(~gender_3cat + FUSNCONSENT_numeric, data = filter(tab2_dt, gender_3cat == "2"))
print(female_xtab)
nonbinary_xtab <- xtabs(~gender_3cat + FUSNCONSENT_numeric, data = filter(tab2_dt, gender_3cat == "3"))
print(nonbinary_xtab)

# Run the chi-squared tests
chi2_test_result_male <- chisq.test(male_xtab)
chi2_test_result_female <- chisq.test(female_xtab)
#chi2_test_result_not_reported <- chisq.test(not_reported_xtab)

# Print the p-values from the chi-squared tests
print(paste("Male p-value: ", chi2_test_result_male$p.value))
print(paste("Female p-value: ", chi2_test_result_female$p.value))
#print(paste("Not reported p-value: ", chi2_test_result_not_reported$p.value))
```

Test for race

```{r}
library(dplyr)

# Filter the data for relevant FUSNCONSENT_numeric values
filtered_data <- tab2_dt %>% filter(FUSNCONSENT_numeric %in% c(0, 7))

# Determine the counts and percentages
race_summary <- filtered_data %>%
  group_by(FUSNCONSENT_numeric, race_4cat) %>%
  summarise(count = n()) %>%
  mutate(total = sum(count),
         percentage = (count / total) * 100) %>%
  ungroup()

print(race_summary)

```

```{r}
table(tab2_dt$race_4cat)
```
```{r}
# Generate cross-tabulations
asian_xtab <- xtabs(~race_4cat + FUSNCONSENT_numeric, data = filter(tab2_dt, race_4cat == "Asian"))
print(asian_xtab)

black_xtab <- xtabs(~race_4cat + FUSNCONSENT_numeric, data = filter(tab2_dt, race_4cat == "Black"))
print(black_xtab)

other_multiple_race_xtab <- xtabs(~race_4cat + FUSNCONSENT_numeric, data = filter(tab2_dt, race_4cat == "Other/Multiple Race"))
print(other_multiple_race_xtab)

white_xtab <- xtabs(~race_4cat + FUSNCONSENT_numeric, data = filter(tab2_dt, race_4cat == "White"))
print(white_xtab)

# Run the chi-squared tests
chi2_test_result_asian <- chisq.test(asian_xtab)
chi2_test_result_black <- chisq.test(black_xtab)
chi2_test_result_other_multiple_race <- chisq.test(other_multiple_race_xtab)
chi2_test_result_white <- chisq.test(white_xtab)

# Print the p-values from the chi-squared tests
print(paste("Asian p-value: ", chi2_test_result_asian$p.value))
print(paste("Black p-value: ", chi2_test_result_black$p.value))
print(paste("Other/Multiple Race p-value: ", chi2_test_result_other_multiple_race$p.value))
print(paste("White p-value: ", chi2_test_result_white$p.value))
```

```{r}
race_xtab <- 
  xtabs(~factor(tab2_dt$race_4cat)+factor(tab2_dt$FUSNCONSENT_numeric))

race_xtab
chisq.test(race_xtab)
chisq.test(race_xtab[c(1, 2, 4),])
```

Test for Ethnicity
```{r}
ethnicity_xtab <- 
  xtabs(~factor(tab2_dt$ethnicity)+factor(tab2_dt$FUSNCONSENT_numeric))

ethnicity_xtab
chisq.test(ethnicity_xtab)
```
```{r}
# Filter the data for relevant FUSNCONSENT_numeric values
filtered_data <- tab2_dt %>% filter(FUSNCONSENT_numeric %in% c(0, 7))

# Determine the counts and percentages
ethnicity_summary <- filtered_data %>%
  group_by(FUSNCONSENT_numeric, ethnicity) %>%
  summarise(count = n()) %>%
  mutate(total = sum(count),
         percentage = (count / total) * 100) %>%
  ungroup()

print(ethnicity_summary)
```


```{r}
# Generate cross-tabulations
Hispanic_xtab <- xtabs(~ethnicity + FUSNCONSENT_numeric, data = filter(tab2_dt, ethnicity == "1"))
print(Hispanic_xtab)

Non_Hispanic_xtab <- xtabs(~ethnicity + FUSNCONSENT_numeric, data = filter(tab2_dt, ethnicity == "2"))
print(Non_Hispanic_xtab)

# Run the chi-squared tests
chi2_test_result_hispanic <- chisq.test(Hispanic_xtab)
chi2_test_result_non_hispanic <- chisq.test(Non_Hispanic_xtab)


# Print the p-values from the chi-squared tests
print(paste("Hispanic p-value: ", chi2_test_result_hispanic$p.value))
print(paste("Non_hispanic p-value: ", chi2_test_result_non_hispanic$p.value))
```
```{r}
ethnicity_xtab <- 
  xtabs(~factor(tab2_dt$ethnicity)+factor(tab2_dt$FUSNCONSENT_numeric))

ethnicity_xtab
chisq.test(ethnicity_xtab)
```

Test for education

```{r}
table(tab2_dt$education)
```
```{r}
# Generate cross-tabulations
high_school_xtab <- xtabs(~education + FUSNCONSENT_numeric, data = filter(tab2_dt, education == "1"))
print(high_school_xtab)

some_college_xtab <- xtabs(~education + FUSNCONSENT_numeric, data = filter(tab2_dt, education == "2"))
print(some_college_xtab)

college_graduate_xtab <- xtabs(~education + FUSNCONSENT_numeric, data = filter(tab2_dt, education == "3"))
print(college_graduate_xtab)

other_xtab <- xtabs(~education+ FUSNCONSENT_numeric, data = filter(tab2_dt, education == "4"))
print(white_xtab)

# Run the chi-squared tests
chi2_test_result_1 <- chisq.test(high_school_xtab)
chi2_test_result_2 <- chisq.test(some_college_xtab)
chi2_test_result_3 <- chisq.test(college_graduate_xtab)
chi2_test_result_4 <- chisq.test(other_xtab)

# Print the p-values from the chi-squared tests
print(paste("High school p-value: ", chi2_test_result_1$p.value))
print(paste("Some college: ", chi2_test_result_2$p.value))
print(paste("College graduate: ", chi2_test_result_3$p.value))
print(paste("Other: ", chi2_test_result_4$p.value))
```

```{r}
# Filter the data for relevant FUSNCONSENT_numeric values
filtered_data <- tab2_dt %>% filter(FUSNCONSENT_numeric %in% c(0, 7))

# Determine the counts and percentages
education_summary <- filtered_data %>%
  group_by(FUSNCONSENT_numeric, education) %>%
  summarise(count = n()) %>%
  mutate(total = sum(count),
         percentage = (count / total) * 100) %>%
  ungroup()

print(education_summary)
```


```{r}
education_xtab <- 
  xtabs(~factor(tab2_dt$education)+factor(tab2_dt$FUSNCONSENT_numeric))

education_xtab
chisq.test(education_xtab)
```

Test for income

```{r}
table(tab2_dt$income)
```
```{r}
# Generate cross-tabulations
income_10_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "10"))
print(income_10_xtab)

income_11_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "11"))
print(income_11_xtab)

income_4_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "4"))
print(income_4_xtab)

income_5_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "5"))
print(income_5_xtab)

income_6_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "6"))
print(income_6_xtab)

income_7_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "7"))
print(income_7_xtab)

income_8_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "8"))
print(income_8_xtab)

income_9_xtab <- xtabs(~income + FUSNCONSENT_numeric, data = filter(tab2_dt, income == "9"))
print(income_9_xtab)

# Run the chi-squared tests
chi2_test_result_income_10 <- chisq.test(income_10_xtab)
chi2_test_result_income_11 <- chisq.test(income_11_xtab)
chi2_test_result_income_4 <- chisq.test(income_4_xtab)
chi2_test_result_income_5 <- chisq.test(income_5_xtab)
chi2_test_result_income_6 <- chisq.test(income_6_xtab)
chi2_test_result_income_7 <- chisq.test(income_7_xtab)
chi2_test_result_income_8 <- chisq.test(income_8_xtab)
chi2_test_result_income_9 <- chisq.test(income_9_xtab)

# Print the p-values from the chi-squared tests
print(paste("Income 10 p-value: ", chi2_test_result_income_10$p.value))
print(paste("Income 11 p-value: ", chi2_test_result_income_11$p.value))
print(paste("Income 4 p-value: ", chi2_test_result_income_4$p.value))
print(paste("Income 5 p-value: ", chi2_test_result_income_5$p.value))
print(paste("Income 6 p-value: ", chi2_test_result_income_6$p.value))
print(paste("Income 7 p-value: ", chi2_test_result_income_7$p.value))
print(paste("Income 8 p-value: ", chi2_test_result_income_8$p.value))
print(paste("Income 9 p-value: ", chi2_test_result_income_9$p.value))

```

```{r}
# Filter the data for relevant FUSNCONSENT_numeric values
filtered_data <- tab2_dt %>% filter(FUSNCONSENT_numeric %in% c(0, 7))

# Determine the counts and percentages
income_summary <- filtered_data %>%
  group_by(FUSNCONSENT_numeric, income) %>%
  summarise(count = n()) %>%
  mutate(total = sum(count),
         percentage = (count / total) * 100) %>%
  ungroup()

print(income_summary)
```

```{r}
income_xtab <- 
  xtabs(~factor(tab2_dt$income)+factor(tab2_dt$FUSNCONSENT_numeric))

income_xtab
chisq.test(income_xtab)
```

Test for household
```{r}
library(dplyr)


stats_household_size <- tab2_dt %>%
  mutate(household_size_numeric = as.numeric(as.character(household_size))) %>%  # Convert household_size to numeric
  group_by(FUSNCONSENT_numeric) %>%
  summarise(
    mean_household_size = mean(household_size_numeric, na.rm = TRUE),
    sd_household_size = sd(household_size_numeric, na.rm = TRUE)
  )

print(stats_household_size)

```

```{r}
# Convert to numeric
tab2_dt$household_numeric <- as.numeric(as.character(tab2_dt$household_size))

# Split data based on FUSNCONSENT_numeric
group1 <- tab2_dt$household_numeric [tab2_dt$FUSNCONSENT_numeric == 0]
group2 <- tab2_dt$household_numeric[tab2_dt$FUSNCONSENT_numeric == 7]

# Perform t-test
t_test_result <- t.test(group1, group2)

print(t_test_result)
```

test for essential_worker
```{r}
# Filter the data for relevant FUSNCONSENT_numeric values
filtered_data <- tab2_dt %>% filter(FUSNCONSENT_numeric %in% c(0, 7))

# Determine the counts and percentages
essential_worker_summary <- filtered_data %>%
  group_by(FUSNCONSENT_numeric, essential_worker) %>%
  summarise(count = n()) %>%
  mutate(total = sum(count),
         percentage = (count / total) * 100) %>%
  ungroup()

print(essential_worker_summary)
```

```{r}
essential_worker_xtab <- 
  xtabs(~factor(tab2_dt$essential_worker)+factor(tab2_dt$FUSNCONSENT_numeric))

essential_worker_xtab
chisq.test(essential_worker_xtab)
```

test for cdc average guideline 

```{r}
data_loc <- "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT/"
eda_env <- readRDS(paste0(data_loc, "eda_objects.rds"))
cdc_scores <- eda_env$cdc_scores

# Extract the cdc_scores for participants with FUSNCONSENT_numeric values of 7 and 0
eda_env$cdc_scores = as.numeric(unlist(eda_env$cdc_scores))
scores_7 <- eda_env$cdc_scores[tab2_dt$FUSNCONSENT_numeric == 7]
scores_0 <- eda_env$cdc_scores[tab2_dt$FUSNCONSENT_numeric == 0]

# Compute mean for each group
mean_scores_7 <- mean(scores_7, na.rm = TRUE)
mean_scores_0 <- mean(scores_0, na.rm = TRUE)

sd_scores_7 <- sd(scores_7, na.rm = TRUE)
sd_scores_0 <- sd(scores_0, na.rm = TRUE)


cat("Mean CDC Score for FUSNCONSENT_numeric == 7:", mean_scores_7, "\n")
cat("Mean CDC Score for FUSNCONSENT_numeric == 0:", mean_scores_0, "\n")

cat("SD CDC Score for FUSNCONSENT_numeric == 7:", sd_scores_7, "\n")
cat("SD CDC Score for FUSNCONSENT_numeric == 0:", sd_scores_0, "\n")
```

```{r}
eda_env$cdc_scores = as.numeric(unlist(eda_env$cdc_scores))

t.test(eda_env$cdc_scores[tab2_dt$FUSNCONSENT_numeric == 7],
      eda_env$cdc_scores[tab2_dt$FUSNCONSENT_numeric == 0]
       )
```

Test for covid_test
```{r}
# Filter the data for relevant FUSNCONSENT_numeric values
filtered_data <- tab2_dt %>% filter(FUSNCONSENT_numeric %in% c(0, 7))

# Determine the counts and percentages
covid_test_summary <- filtered_data %>%
  group_by(FUSNCONSENT_numeric, covid_test) %>%
  summarise(count = n()) %>%
  mutate(total = sum(count),
         percentage = (count / total) * 100) %>%
  ungroup()

print(covid_test_summary)
```

```{r}
covid_test_xtab <- 
  xtabs(~factor(tab2_dt$covid_test)+factor(tab2_dt$FUSNCONSENT_numeric))

covid_test_xtab
chisq.test(covid_test_xtab)
```


Test for positive covid -- tab2_dt$covid_test == 1

```{r}
# Filter the data for relevant FUSNCONSENT_numeric values
filtered_data <- tab2_dt %>% filter(FUSNCONSENT_numeric %in% c(0, 7) & covid_test == 1)

# Determine the counts and percentages
covid_test_summary <- filtered_data %>%
  group_by(FUSNCONSENT_numeric, covid_test) %>%
  summarise(count = n()) %>%
  mutate(total = sum(count),
         percentage = (count / total) * 100) %>%
  ungroup()

print(covid_test_summary)

```

```{r}
positive_covid_xtab <- xtabs(~covid_test + FUSNCONSENT_numeric, data = filter(tab2_dt, covid_test == "1"))
chisq.test(positive_covid_xtab)
```

```{r}
daily_drinking_xtab <- 
  xtabs(~factor(tab2_dt$daily_drinking, exclude = NULL)+
          factor(tab2_dt$FUSNCONSENT_numeric))

daily_drinking_xtab
chisq.test(daily_drinking_xtab)
```


```{r}
daily_opioid_xtab <- 
  xtabs(~factor(tab2_dt$daily_opioid, exclude = NULL)+
          factor(tab2_dt$FUSNCONSENT_numeric))

daily_opioid_xtab
chisq.test(daily_opioid_xtab)
```


```{r}
daily_stimulant_xtab <- 
  xtabs(~factor(tab2_dt$daily_stimulant, exclude = NULL)+
          factor(tab2_dt$FUSNCONSENT_numeric))

daily_stimulant_xtab
chisq.test(daily_stimulant_xtab)
```

read the cdc_score data

```{r}
data_loc <- "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT/"
eda_env <- readRDS(paste0(data_loc, "eda_objects.rds"))
cdc_scores <- eda_env$cdc_scores
```


Quartiles for age

```{r}
# Check lengths
length_of_filtered_cdc_scores <- length(cdc_scores_numeric[tab2_dt$FUSNCONSENT_numeric == 7])
length_of_filtered_age <- nrow(tab2_dt[tab2_dt$FUSNCONSENT_numeric == 7, ])

cat("Length of filtered cdc_scores:", length_of_filtered_cdc_scores, "\n")
cat("Length of filtered age:", length_of_filtered_age, "\n")

# If they are different, we'll need to investigate further
if(length_of_filtered_cdc_scores != length_of_filtered_age) {
  cat("Discrepancy found! Investigating...\n")

  # Check for NAs
  na_in_cdc_scores <- sum(is.na(cdc_scores_numeric[tab2_dt$FUSNCONSENT_numeric == 7]))
  na_in_FUSNCONSENT_numeric <- sum(is.na(tab2_dt$FUSNCONSENT_numeric))

  cat("Number of NAs in filtered cdc_scores:", na_in_cdc_scores, "\n")
  cat("Number of NAs in FUSNCONSENT_numeric:", na_in_FUSNCONSENT_numeric, "\n")
}

```

```{r}
# Filter cdc_scores based on FUSNCONSENT_numeric from tab2_dt
filtered_cdc_scores <- data.frame(cdc_scores = cdc_scores_numeric[tab2_dt$FUSNCONSENT_numeric == 7])

# Remove NAs from filtered cdc_scores
filtered_cdc_scores <- filtered_cdc_scores %>% filter(!is.na(cdc_scores))

# Compute quartiles for these filtered scores
filtered_cdc_scores <- filtered_cdc_scores %>%
  mutate(cdc_quartiles = ntile(cdc_scores, 4))

# Create a data frame from the age list in the environment and convert to numeric
age_df <- tab2_dt %>%
  filter(FUSNCONSENT_numeric == 7) %>%
  mutate(age_numeric = as.numeric(as.character(age))) %>%
  select(age_numeric)

# Check lengths again
cat("Length of cleaned filtered cdc_scores:", nrow(filtered_cdc_scores), "\n")
cat("Length of filtered age:", nrow(age_df), "\n")

# Assuming the lengths match, combine cdc_scores and age into one data frame
if (nrow(filtered_cdc_scores) == nrow(age_df)) {
  combined_df <- cbind(filtered_cdc_scores, age_df)
  
  # Compute summary statistics for age within each quartile
  age_summary <- combined_df %>%
    group_by(cdc_quartiles) %>%
    summarise(age_mean = mean(age_numeric, na.rm = TRUE),
              age_sd = sd(age_numeric, na.rm = TRUE))
    
  print(age_summary)
} else {
  cat("The lengths do not match! Further investigation is required.")
}


```

Quartiles for Gender

```{r}
# Convert cdc_scores to numeric and create a data frame
cdc_df <- data.frame(cdc_scores = as.numeric(unlist(eda_env$cdc_scores)))

# Apply the ntile function to create quartiles
cdc_df <- cdc_df %>%
  mutate(cdc_quartiles = ntile(cdc_scores, 4))

# Create a data frame from the gender list in the environment
gender_df <- data.frame(gender = unlist(tab2_dt$gender))

# Combine cdc_scores and gender into one data frame
combined_df <- cbind(cdc_df, gender_df)

# Compute quartiles for cdc_scores within each gender category
gender_summary <- combined_df %>%
  group_by(gender) %>%
  summarise(
    Q1 = quantile(cdc_scores, 0.25, na.rm = TRUE),
    Q2 = quantile(cdc_scores, 0.5, na.rm = TRUE),
    Q3 = quantile(cdc_scores, 0.75, na.rm = TRUE),
    Q4 = quantile(cdc_scores, 1, na.rm = TRUE)
  )
  
print(gender_summary)
```