---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

Test hypothesis that COVID behavior scores (continuously or dummy coded) are significantly correlated with COVID protection behaviors among the agents. 

## Load libraries, set working directory, and dataset used in descriptive analysis

```{r, echo=FALSE, message=FALSE}
rm(list=ls())
library(haven)
library(dplyr)
library(data.table)
library(lme4)
library(geeM)
```

Set the working directory:

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT")
```

Read the datasets:

```{r, include=FALSE}
network_env <- readRDS("network_objects.rds")
sns_dt_long_wide_no_minors <- network_env$sns_dt_long_wide_no_minors

eda_env <- readRDS("eda_objects.rds")
tab2_dt <- as.data.table(eda_env$tab2_dt)
cdc_scores <- eda_env$cdc_scores
vh_scores <- eda_env$vh_info_scores

tab2_dt$MTURKID <- as.factor(tab2_dt$MTURK1)
```

Query the dataset:

```{r}
#View(sns_dt_long_wide_no_minors)
colnames(sns_dt_long_wide_no_minors)
```

Demographics on the egos are present in the `tab2_dt` object in the `eda_env` environment.


Merge ego demographics into long form network dataset:

```{r}
sns_dt_long_merged_ego_characteristics <- merge(sns_dt_long_wide_no_minors, tab2_dt, by="MTURKID")
class(sns_dt_long_merged_ego_characteristics)
#sns_dt_long_merged_ego_characteristics$MTURKID <- as.factor(sns_dt_long_merged_ego_characteristics$MTURKID)

sns_dt_long_merged_ego_characteristics[,age := as.numeric(age)]
```

Merge in the component outcomes of the the CDC average score:

```{r}
sns_dt_long_merged_ego_characteristics <- merge(sns_dt_long_merged_ego_characteristics,
                                                    cdc_scores %>% select(-cdc_avg_out),
                                                    by = "MTURKID")
```

Component variables of social network score:

- If the network member has been tested for COVID-19 (SN27)
- If the network member has tested positive for COVID-19 (SN27a), 
- If the network member has been hospitalized for COVID-19 (SN27a1)
- If the network member knows anyone who has been hospitalized for
COVID-19 (SN28),
- If the network member knows anyone who has died of COVID-19 (SN29),
- if the network member has ever encouraged the participant to get tested
for COVID-19 (SN32),
- If the network member follows social distancing guidelines (SN33),
- If the network member has encouraged the participant to follow social
distancing guidelines (SN34)
- If the network member has received at least one dose of the COVID-19
vaccine (SN37), if the network member had a negative reaction or bad
side effects after the COVID-19 vaccine (SN37a), if the network member
is open to receiving a vaccine (SN37b),
- If the network member has encouraged the participant to get the COVID-19
vaccine (SN38),
- If the network member has discouraged the participant from getting the
COVID-19 vaccine (SN39).


## Association of COVID Behaviors among Egos with Alter Attitudes/Behaviors 


```{r}

# Create a new variable that is the reverse of SN27,... and coded as 0 and 1
sns_dt_long_merged_ego_characteristics$SN27_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN27 == 1, 1, 0)
sns_dt_long_merged_ego_characteristics$SN28_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN28 == 1, 1, 0)
sns_dt_long_merged_ego_characteristics$SN29_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN29 == 1, 1, 0)
sns_dt_long_merged_ego_characteristics$SN33_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN33 == 1, 1, 0)
sns_dt_long_merged_ego_characteristics$SN34_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN34 == 1, 1, 0)
sns_dt_long_merged_ego_characteristics$SN37_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN37 == 1, 1, 0)
sns_dt_long_merged_ego_characteristics$SN38_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN38 == 1, 1, 0)
sns_dt_long_merged_ego_characteristics$SN39_reversed <- ifelse(sns_dt_long_merged_ego_characteristics$SN39 == 1, 1, 0)


# Check the frequencies of the new variable
table(sns_dt_long_merged_ego_characteristics$SN27_reversed, exclude = NULL)

# Specify correlation structure
corstr <- "exchangeable"

## SN27
m1_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN27, id = MTURKID, family="binomial", corstr = corstr)
summary(m1_gee_disc)

m1_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN27_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m1_gee_disc_reversed)

## SN28
m2_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN28, id = MTURKID, family="binomial", corstr = corstr)
summary(m2_gee_disc)

m2_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN28_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m2_gee_disc_reversed)

## SN29
m2a_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN29, id = MTURKID, family="binomial", corstr = corstr)
summary(m2a_gee_disc)

m2a_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN29_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m2a_gee_disc_reversed)


## SN33
m3_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN33, id = MTURKID, family="binomial", corstr = corstr)
summary(m3_gee_disc)

m3_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN33_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m3_gee_disc_reversed)

## SN34
m4_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN34, id = MTURKID, family="binomial", corstr = corstr)
summary(m4_gee_disc)

m4_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN34_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m4_gee_disc_reversed)

## m5
m5_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN37, id = MTURKID, family="binomial", corstr = corstr)
summary(m5_gee_disc)

m5_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN37_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m5_gee_disc_reversed)


## m6
m6_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN38, id = MTURKID, family="binomial", corstr = corstr)
summary(m6_gee_disc)

m6_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN38_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m6_gee_disc_reversed)

## m7
m7_gee_disc <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN39, id = MTURKID, family="binomial", corstr = corstr)
summary(m7_gee_disc)

m7_gee_disc_reversed <- 
  geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN39_reversed, id = MTURKID, family="binomial", corstr = corstr)
summary(m7_gee_disc_reversed)

## include all covariates
model_disc_gee_reversed <- geem(data=sns_dt_long_merged_ego_characteristics, cdc_avg_out_adequate ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed + SN33_reversed + 
                   SN34_reversed + SN37_reversed + SN38_reversed, id = MTURKID, family="binomial",
                 corstr = corstr)
summary(model_disc_gee_reversed)

```

Component Outcomes of CDC Score:

1. Wash your hands often with soap and water for at least 20 seconds especially after you have been in a public place, or after blowing your nose, coughing, or sneezing? (CDC1) 
2. Use hand sanitizer that contains at least 60% alcohol when soap and water was not readily available? (CDC2) 
3. Avoid touching your eyes, nose, and mouth? (CDC3) 
4. Avoid close contact with people who are sick? (CDC4) 
5. Remain at least 6 feet away from other people when in public? (CDC5) 
6.Stay home as much as possible? (CDC6) 
7. Use a cloth face cover over your nose and mouth when in public? (CDC7) 
8. Cover your mouth and nose with a tissue or use the inside of your elbow when you coughed or sneezed? (CDC8) 
9. Throw used tissues in the trash? (CDC9) 
10. Immediately wash your hands with soap and water for at least 20 seconds after coughing or sneezing? (CDC10) 
11. Clean and disinfectant frequently touched surfaces in your home (examples: tables, doorknobs, light switches, countertops, desks, phones, toilets, faucets)? (CDC11) 
12. Use detergent or soap and water to clean dirty surfaces before disinfection? (CDC12) 
13. When cleaning surfaces, how often did you use any of the following: a diluted household bleach, a solution that was at least 70% alcohol, or another EPA-registered household disinfect? (CDC13) 

```{r}
sns_dt_long_merged_ego_characteristics$cdc1_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC1 > 2, 1, 0)

model_cdc1 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc1_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc1)

sns_dt_long_merged_ego_characteristics$cdc2_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC2 > 2, 1, 0)

model_cdc2 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc2_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc2)

sns_dt_long_merged_ego_characteristics$cdc3_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC3 > 2, 1, 0)
model_cdc3 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc3_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc3)

sns_dt_long_merged_ego_characteristics$cdc4_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC4 > 2, 1, 0)
model_cdc4 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc4_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc4)

sns_dt_long_merged_ego_characteristics$cdc5_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC5 > 2, 1, 0)
model_cdc5 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc5_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc5)

sns_dt_long_merged_ego_characteristics$cdc6_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC6 > 2, 1, 0)
model_cdc6 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc6_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc6)

sns_dt_long_merged_ego_characteristics$cdc7_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC7 > 2, 1, 0)
model_cdc7 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc7_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc7)

sns_dt_long_merged_ego_characteristics$cdc8_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC8 > 2, 1, 0)
model_cdc8 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc8_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc8)

sns_dt_long_merged_ego_characteristics$cdc9_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC9 > 2, 1, 0)
model_cdc9 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc9_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc9)

sns_dt_long_merged_ego_characteristics$cdc10_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC10 > 2, 1, 0)
model_cdc10 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc10_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc10)

sns_dt_long_merged_ego_characteristics$cdc11_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC11 > 2, 1, 0)
model_cdc11 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc11_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc11)

sns_dt_long_merged_ego_characteristics$cdc12_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC12 > 2, 1, 0)
model_cdc12 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc12_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc12)

### EXCHANGEABLE CORSTR PRODUCES WARNINGS
sns_dt_long_merged_ego_characteristics$cdc13_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$CDC12 > 2, 1, 0)
model_cdc13 <- geem(data=sns_dt_long_merged_ego_characteristics, cdc13_adequate ~ 
                 SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_cdc13)
```

# ```{r}
# model_cont_gee <- geem(cdc_avg_out ~ SN27 + SN28 + SN29 + SN33 + SN34 + SN37 + SN38, 
#                   id=MTURKID, data=sns_dt_long_merged_ego_characteristics, 
#                   family=gaussian, corstr="exchangeable")
# 
# summary(model_cont_gee)
# ```

## Association of Vaccine Hesitance among Egos with Alter Attitudes/Behaviors

### Merge datasets

```{r}
sns_dt_long_merged_ego_characteristics <- merge(sns_dt_long_merged_ego_characteristics,
                                                    vh_scores,
                                                    by = "MTURKID")
```


### Test associations

```{r}
sns_dt_long_merged_ego_characteristics$vh1_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$vh1 < 2, 1, 0)

model_vh1 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed +
                   SN34_reversed + SN38_reversed,
                 #+ SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_vh1)

model_vh1_sn27 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN27_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn27)

model_vh1_SN28 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN28)

model_vh1_SN29 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN29_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN29)

model_vh1_sn33 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN33_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1)

model_vh1_SN34 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN28)

model_vh1_sn37 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN37_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn37)

model_vh1_SN38 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN38_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN38)

#model_vh1_SN39 <- geem(data=sns_dt_long_merged_ego_characteristics, 
 #                 vh1_adequate ~ SN39_reversed,
  #               family="binomial", corstr = corstr)
#summary(model_vh1_SN39)
```

