---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

We present the nearest neighbor analysis below. 

Set working directory:

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT")
```

```{r}
library(haven)
library(igraph)
library(dplyr)
library(data.table)
library(RColorBrewer)
```

Read social network data with minors removed, including MTURK IDs for participants 
and faux-IDs for alters:

```{r}
rm(list=ls())
sns_dt_read <- readRDS("sns_dt_long_wide_no_minors.RDS")
dim(sns_dt_read)
class(sns_dt_read)
```

We follow ideas from [Kolaczyk](https://paperpile.com/app/p/c70e3441-d39c-0d0c-9f1f-f476139d2e86), 
Chapter 8, to conduct this analysis.

Initialize data as an `igraph` object:

```{r}
ig <- graph_from_data_frame(d = sns_dt_read, directed = TRUE)
ig
```

Number of edges and vertices respectively:

```{r}
gorder(ig) #num nodes
gsize(ig) #num edges
```

We know that there are 

```{r}
length(unique(sns_dt_read$MTURKID))
``` 
participants who reported data on 

```{r}
length(unique(sns_dt_read$alterID))
```
adult network members.

We can verify that the sum of the above two quantities is the total number of 
nodes in the network:

```{r}
length(unique(sns_dt_read$MTURKID)) + length(unique(sns_dt_read$alterID)) ==
  gorder(ig)
```
Add vertex attributes to `ig`. To do this, we first want to pull out the 
alter IDs and the attributes in the `sns_dt_read` dataset above, and convert it 
to long format. 

```{r}
net_dt_wide <- sns_dt_read[, !c("MTURKID", "comp_code_Text_Set")]
dim(net_dt_wide)
```

The next steps is to extract the relevant individual attributes of the 173 participants who
provided data on their social networks:

```{r}
consenting_network_participant_dt <- readRDS("sns_consenting_dt.RDS")
dim(consenting_network_participant_dt)
```

Dataset on other individual-level variables for all participants who completed
the baseline survey:

<!-- ```{r} -->
<!-- all_participant_dt <- readRDS("participant_dt_wide.RDS") -->
<!-- ``` -->

# Nearest Neighbor Analysis

## Compiling alter data in igraph data structure

First, we need to see what vertex attributes our graph object has:

```{r}
vertex_attr_names(ig)
```

Currently, `ig` only has the `r vertex_attr_names(ig)`vertex attribute. Other vertex attributes need to be added. 

```{r}
summary(sns_dt_read$SN37)
length(sns_dt_read$SN37)
```

Let's add alter attributes to the graph,
from the `sns_dt_read` dataset. Use the
Stack Overflow ideas here: https://stackoverflow.com/questions/49728990/how-can-i-add-a-data-frame-as-vertex-attributes-with-matching-ids-in-igraph. 

Start by converting the `ig` object to a dataframe, so we
can perform a `join` operation later. The `both` argument ensures
that the vertices and edges are converted to a data frame and 
appended sequentially in a list. 

```{r}
ig_df <- igraph::as_data_frame(ig, 'both')
```



```{r}
summary(ig_df)
class(ig_df)
length(ig_df)
names(ig_df)
```

Now query the `ig_df$vertices` data frame:

```{r}
colnames(ig_df$vertices)
dim(ig_df$vertices)
str(ig_df$vertices)
```

Append the column data for alter IDs from `sns_dt_read` to the
`ig_df$vertices` datafame.

```{r}
ig_df$vertices <- ig_df$vertices %>% 
  left_join(sns_dt_read, c('name'='alterID'))

class(ig_df$vertices)
dim(ig_df$vertices)
colnames(ig_df$vertices)
```


The `ig_df$vertices` data frame does not have
any ego attribute data yet. 

Convert the data frame back to a graph object: 

```{r}
updated_alterdt_ig <- graph_from_data_frame(ig_df$edges,
                                   directed = TRUE,
                                   vertices = ig_df$vertices)

summary(updated_alterdt_ig)
```

Check the vertex attributes:

```{r}
vertex_attr_names(updated_alterdt_ig)
```

```{r}
table(V(updated_alterdt_ig)$SN37, exclude = NULL)
```

```{r}

V(updated_alterdt_ig)$SN37[1:10]
#V(updated_alterdt_ig)[SN37 == 1]$color <- "yellow"
#V(updated_alterdt_ig)[SN37 == 1]$color <- "yellow"
#V(updated_alterdt_ig)[SN37 == 2]$color <- "blue"

```

```{r}

pal <- brewer.pal(length(unique(V(updated_alterdt_ig)$SN37)), "Dark2")
plot(updated_alterdt_ig, 
     vertex.color = pal[as.numeric(as.factor(vertex_attr(updated_alterdt_ig, "SN37")))])
```



