---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

Test hypothesis that Vaccine acceptance/hesitancy scores (continuously or dummy coded) for the egos are significantly correlated with 
COVID behaviors among the social network contacts. 

## Load libraries, set working directory, and dataset used in descriptive analysis

```{r, echo=FALSE, message=FALSE}
rm(list=ls())
library(haven)
library(dplyr)
library(data.table)
library(lme4)
library(geeM)
```

Set the working directory:

```{r, setup, include=FALSE}
data_loc <- "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT/"
```

Read the datasets:

```{r, include=FALSE}
merged_network_participant_env <- 
  readRDS(paste0(data_loc, "merged_network_participant_objects.rds"))

sns_dt_long_merged_ego_characteristics <- merged_network_participant_env$sns_dt_long_merged_ego_characteristics

```

Query the dataset:

```{r}
head(colnames(sns_dt_long_merged_ego_characteristics), 10)
```


## Association of Vaccine Hesitance among Egos with Alter Attitudes/Behaviors



### Test associations

```{r}
# Specify correlation structure
corstr <- "exchangeable"
```

VH1: Plans to take COVID vaccine 

```{r}
sns_dt_long_merged_ego_characteristics$vh1_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$vh1 < 2, 1, 0)

model_vh1 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed +
                   SN34_reversed + SN38_reversed,
                 #+ SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_vh1)

model_vh1_sn27 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN27_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn27)

model_vh1_SN9 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN9,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN9)

model_vh1_SN28 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN28)

model_vh1_SN29 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN29_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN29)

# model_vh1_sn33 <- geem(data=sns_dt_long_merged_ego_characteristics, 
#                   vh1_adequate ~ SN33_reversed,
#                  family="binomial", corstr = corstr)
# summary(model_vh1)

model_vh1_SN34 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN28)

model_vh1_sn37 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN37_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn37)

model_vh1_SN38 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN38_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN38)

#model_vh1_SN39 <- geem(data=sns_dt_long_merged_ego_characteristics, 
 #                 vh1_adequate ~ SN39_reversed,
  #               family="binomial", corstr = corstr)
#summary(model_vh1_SN39)
```

VH3: attitude towards receiving a COVID-19 

```{r}
sns_dt_long_merged_ego_characteristics$vh3_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$vh3 <= 2, 1, 0)

model_vh3 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed +
                   SN33_reversed+
                   SN34_reversed + SN37_reversed + SN38_reversed,
                 #+ SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_vh3)

model_vh3_SN9 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN9,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN9)

model_vh3_sn27 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN27_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_sn27)

model_vh3_SN28 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN28)

model_vh3_SN29 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN29_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN29)

model_vh3_sn33 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN33_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_sn33)

model_vh3_SN34 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN34_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN34)

model_vh3_sn37 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN37_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_sn37)

model_vh3_SN38 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh3_adequate ~ SN38_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN38)

#model_vh3_SN39 <- geem(data=sns_dt_long_merged_ego_characteristics, 
#                  vh3_adequate ~ SN39_reversed,
#                   family="binomial", corstr = corstr)
# summary(model_vh3_SN39)
```
