---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

Test hypothesis that Vaccine acceptance/hesitancy scores (continuously or dummy coded) for the egos are significantly correlated with 
COVID behaviors among the social network contacts. 

## Load libraries, set working directory, and dataset used in descriptive analysis

```{r, echo=FALSE, message=FALSE}
rm(list=ls())
library(haven)
library(dplyr)
library(data.table)
library(geeM)
```

Set the working directory:

```{r, setup, include=FALSE}
data_loc <- "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT/"
```

Read the datasets:

```{r, include=FALSE}
vaccine_access_env <- 
  readRDS(paste0(data_loc, "vaccine_access_env.rds"))

regression_dt <- vaccine_access_env$regression_dt

```

Query the dataset:

```{r}
head(colnames(regression_dt), 10)
```


## Association of Vaccine Hesitance among Egos with Alter Attitudes/Behaviors



### Test associations

```{r}
# Specify correlation structure
corstr <- "exchangeable"
```

VH1: Plans to take COVID vaccine 

```{r}

table(regression_dt$vh1, exclude = NULL)
# o	Definitely  (1) 
# o	Probably  (2) 
# o	I may or I may not  (3) 
# o	Probably not  (4) 
# o	Definitely not  (5) 
# o	Don't know  (6) 

regression_dt$vh1_adequate <- 
  ifelse(regression_dt$vh1 < 2, 1, 0) # only definitely is coded 1, else 0

model_vh1 <- geem(data=regression_dt, 
                  vh1_adequate ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed +
                   SN34_reversed + SN38_reversed,
                 #+ SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_vh1)

model_vh1_sn27 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN27_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn27)

model_vh1_SN9 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN9_recoded,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN9)

model_vh1_SN28 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN28)

model_vh1_SN29 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN29_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN29)

model_vh1_SN32 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN32_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN32)

sum(is.na(regression_dt$vh1_adequate))
sum(is.na(regression_dt$SN32_reversed))
# model_vh1_sn33 <- geem(data=regression_dt, 
#                   vh1_adequate ~ SN33_reversed,
#                  family="binomial", corstr = corstr)
# summary(model_vh1)

model_vh1_SN34 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN34_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN34)

model_vh1_sn37 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN37_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn37)

model_vh1_SN38 <- geem(data=regression_dt, 
                  vh1_adequate ~ SN38_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN38)

# model_vh1_SN39 <- geem(data=regression_dt,
#                 vh1_adequate ~ SN39_reversed,
#               family="binomial", corstr = corstr)
# summary(model_vh1_SN39)
```

VH3: attitude towards receiving a COVID-19 

```{r}

# VH3 I would describe my attitude towards receiving a COVID-19 vaccine as:
# o	Very positive  (1) 
# o	Pretty positive  (2) 
# o	Neutral  (3) 
# o	Pretty Negative  (4) 
# o	Very Negative  (5) 
# o	Don't know  (6) 

regression_dt$vh3_adequate <- 
  ifelse(regression_dt$vh3 <= 2, 1, 0) #very/pretty positive = 1, else 0

model_vh3 <- geem(data=regression_dt, 
                  vh3_adequate ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed +
                   SN33_reversed+
                   SN34_reversed + SN37_reversed + SN38_reversed,
                 #+ SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_vh3)

model_vh3_age <- geem(data=regression_dt, 
                  vh3_adequate ~ age,
                 family="binomial", corstr = corstr)
summary(model_vh3_age)

# model_vh3_income_category <- geem(data=regression_dt, 
#                   vh3_adequate ~ income_category, #does not converge
#                  family="binomial", corstr = corstr)
# summary(model_vh3_income_category)

model_vh3_SN9 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN9_recoded,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN9)


model_vh3_sn27 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN27_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_sn27)

model_vh3_SN28 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN28)

model_vh3_SN29 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN29_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN29)

model_vh3_SN32 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN32_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN32)

model_vh3_sn33 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN33_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_sn33)

model_vh3_SN34 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN34_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN34)

model_vh3_sn37 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN37_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_sn37)

model_vh3_SN38 <- geem(data=regression_dt, 
                  vh3_adequate ~ SN38_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh3_SN38)

# model_vh3_SN39 <- geem(data=regression_dt,
#                  vh3_adequate ~ SN39_reversed,
#                   family="binomial", corstr = corstr)
# summary(model_vh3_SN39)
```
