---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

Test hypothesis that Vaccine acceptance/hesitancy scores (continuously or dummy coded) for the egos are significantly correlated with 
COVID behaviors among the social network contacts. 

## Load libraries, set working directory, and dataset used in descriptive analysis

```{r, echo=FALSE, message=FALSE}
rm(list=ls())
library(haven)
library(dplyr)
library(data.table)
library(lme4)
library(geeM)
library(igraph)
```

Set the working directory:

```{r, setup, include=FALSE}
data_loc <- "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT/"
```

Read the datasets:

```{r, include=FALSE}

eda_env <- readRDS(paste0(data_loc, "eda_objects.rds"))
full_ego_dt <- eda_env[["dt"]]

merged_network_participant_env <- 
  readRDS(paste0(data_loc, "merged_network_participant_objects.rds"))


sns_dt_long_merged_ego_characteristics <- 
  merged_network_participant_env$sns_dt_long_merged_ego_characteristics

vacces_info_scores <- eda_env$vaccess_info_scores

full_dt <- eda_env$dt

## merging
sns_dt_long_merged_ego_characteristics <- merge(sns_dt_long_merged_ego_characteristics,
                                                   vacces_info_scores,
                                                    by = "MTURKID")
```

Query the dataset:

```{r}
head(colnames(full_dt), 10)
head(colnames(sns_dt_long_merged_ego_characteristics), 10)
```

## Vaccine acceptance reporting among the egos

Variable VA3: summary of whether one shot has been taken for 851 network contacts
Variable VA4: summary of whether vaccine was offered for 851 network contacts

```{r}
(full_dt$FUVA3)
table(full_dt$FUVA3, exclude = NULL)
table(full_dt$FUVA4, exclude = NULL)

xtabs(~factor(FUVA3, exclude = NULL)+factor(FUVA4, exclude = NULL), 
      data = full_dt)

va3_fusnconsent_xtabs <- 
  as.matrix(
    xtabs(~factor(FUVA3, exclude = NULL)+
          factor(FUSNCONSENT, exclude = NULL), 
        data = full_dt)
  )

sweep(va3_fusnconsent_xtabs, 2, colSums(va3_fusnconsent_xtabs), "/")
# straightforward division as va3_fusnconsent_xtabs/colSums...gives the wrong answer
# can be done correctly using apply: 
# `apply(va3_fusnconsent_xtabs, 2, function(column) column/sum(column))`



va3_fusnconsent_xtabs/colSums(va3_fusnconsent_xtabs)

xtabs(~factor(FUVA4, exclude = NULL)+
        factor(FUSNCONSENT, exclude = NULL), 
      data = full_dt)

```

## Vaccination rates among alters/social network contacts

```{r}
table(sns_dt_long_merged_ego_characteristics$SN37, exclude = NULL)
table(sns_dt_long_merged_ego_characteristics$SN37, exclude = NULL)/sum(
  table(sns_dt_long_merged_ego_characteristics$SN37, exclude = NULL))
```


## Homophily on vaccination status 

Computation:

```{r}
# Compute homophily

## prep data
ego_snconsenting_dt <- full_dt %>%
  filter(FUSNCONSENT == 7)
dim(ego_snconsenting_dt)  

head(ego_snconsenting_dt$MTURK1, 25)
table(ego_snconsenting_dt$FUVA3, exclude = NULL) #egos
table(ego_snconsenting_dt$FUSNCONSENT, exclude = NULL) #egos

head(sns_dt_long_merged_ego_characteristics$MTURK1, 25) #alters
table(sns_dt_long_merged_ego_characteristics$SN37, exclude = NULL)

## merge data
ego_alter_paring_merge_dt <-
  #create dataset that merges ego and network information to give unique ego-alter pairs 
  merge(ego_snconsenting_dt, sns_dt_long_merged_ego_characteristics, by = "MTURK1", all.x = TRUE)

dim(ego_alter_paring_merge_dt) #851 rows as expected, since there are 851 ego-alter pairings
colnames(ego_alter_paring_merge_dt)

head(ego_alter_paring_merge_dt) 

### check results of merge
length(unique(ego_alter_paring_merge_dt$MTURK1)) == nrow(ego_snconsenting_dt)
ego_alter_paring_merge_dt[ego_alter_paring_merge_dt$MTURK1 == ego_alter_paring_merge_dt$MTURK1[[1]],]

## compute homophily measure:
### egos vaccination status represented by FUVA3 and alters' represented by SN37

### create a column to indicate if ego and alter share the same vaccination state
ego_alter_paring_merge_dt$same_vaccination_state <- ifelse(
  ego_alter_paring_merge_dt$FUVA3 == ego_alter_paring_merge_dt$SN37, 1, 0)

### create a frequency table
frequency_table <- table(ego_alter_paring_merge_dt$same_vaccination_state, exclude = NULL)
print(frequency_table)

### compute proportions 
proportion_table <- frequency_table / sum(frequency_table)
print(proportion_table)


```

Plotting:

```{r}

# create unique identifiers for egos and alters

## copy original MTURK Ids
ego_snconsenting_dt$original_MTurk <- ego_snconsenting_dt$MTURK1
sns_dt_long_merged_ego_characteristics$original_MTurk <- sns_dt_long_merged_ego_characteristics$MTURK1

## ego ID
ego_snconsenting_dt$MTURK1 <- paste0("E_", ego_snconsenting_dt$MTURK1) 


## alter ID
sns_dt_long_merged_ego_characteristics <- sns_dt_long_merged_ego_characteristics %>%
  group_by(original_MTurk) %>%
  mutate(seq = row_number())
sns_dt_long_merged_ego_characteristics$MTURK1 <- paste0("A_", sns_dt_long_merged_ego_characteristics$original_MTurk, "_", 
                                                        sns_dt_long_merged_ego_characteristics$seq)

## merge
ego_alter_paring_merge_dt <- merge(ego_snconsenting_dt, sns_dt_long_merged_ego_characteristics, by = "original_MTurk", all.x = TRUE)

## create graph
g <- graph_from_data_frame(d=ego_alter_paring_merge_dt[, c("MTURK1.x", "MTURK1.y")], directed=FALSE)

#print(g)
vcount(g)
ecount(g)

#colors
V(g)$color <- ifelse(V(g)$name %in% ego_snconsenting_dt$MTURK1, 
                    ifelse(ego_snconsenting_dt$FUVA3 == 1, "green", "red"), 
                    ifelse(sns_dt_long_merged_ego_characteristics$SN37 == 1, "green", "red")
)
                    #red=unvaccinated, green=vaccinated

#layout
layout <- layout_with_kk(g)

# Plot the network
plot(g, 
     layout = layout, 
     vertex.size = 7, 
     vertex.label = NA, 
     edge.arrow.size = 0.5, 
     edge.color = "gray50", 
     main = "Network Diagram")


```

## Association of Vaccine Access among Egos with Alter Attitudes/Behaviors

```{r}
table(sns_dt_long_merged_ego_characteristics$va3, exclude = NULL)

table(sns_dt_long_merged_ego_characteristics$va4, exclude = NULL)

xtabs(~factor(va3, exclude = NULL)+factor(va4, exclude = NULL), 
      data = sns_dt_long_merged_ego_characteristics)

xtabs(~factor(va3, exclude = NULL)+factor(FUSNCONSENT, exclude = NULL), 
      data = sns_dt_long_merged_ego_characteristics)

xtabs(~factor(va4, exclude = NULL)+factor(FUSNCONSENT, exclude = NULL), 
      data = sns_dt_long_merged_ego_characteristics)

```


### Test associations

```{r}
# Specify correlation structure
corstr <- "exchangeable"
```

VA3: Taken at least one dose of the vaccine

```{r}
#sns_dt_long_merged_ego_characteristics$vh1_adequate <- 
#  ifelse(sns_dt_long_merged_ego_characteristics$vh1 < 2, 1, 0)

# Recode the binary outcome
sns_dt_long_merged_ego_characteristics$va3 <- 
  ifelse(sns_dt_long_merged_ego_characteristics$va3 == 2, 0, 1)

# Check the recoded table
table(sns_dt_long_merged_ego_characteristics$va3, exclude = NULL)

model_va3 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed +
                   SN34_reversed + SN38_reversed,
                 #+ SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_va3)

model_va3_sn27 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ SN27_reversed,
                 family="binomial", corstr = corstr)
summary(model_va3_sn27)

model_va3_SN9 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ SN9,
                 family="binomial", corstr = corstr)
summary(model_va3_SN9)

model_va3_SN28 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_va3_SN28)

model_va3_SN29 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ SN29_reversed,
                 family="binomial", corstr = corstr)
summary(model_va3_SN29)

# model_va3_sn33 <- geem(data=sns_dt_long_merged_ego_characteristics, 
#                   va3 ~ SN33_reversed,
#                  family="binomial", corstr = corstr)
# summary(model_va3)

model_va3_SN34 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_va3_SN28)

model_va3_sn37 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ SN37_reversed,
                 family="binomial", corstr = corstr)
summary(model_va3_sn37)

model_va3_SN38 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  va3 ~ SN38_reversed,
                 family="binomial", corstr = corstr)
summary(model_va3_SN38)

#model_va3_SN39 <- geem(data=sns_dt_long_merged_ego_characteristics, 
 #                 va3 ~ SN39_reversed,
  #               family="binomial", corstr = corstr)
#summary(model_va3_SN39)
```

VH3: attitude towards receiving a COVID-19 

