---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

Test hypothesis that Vaccine acceptance/hesitancy scores (continuously or dummy coded) for the egos are significantly correlated with 
COVID behaviors among the social network contacts. 

## Load libraries, set working directory, and dataset used in descriptive analysis

```{r, echo=FALSE, message=FALSE}
rm(list=ls())
library(haven)
library(dplyr)
library(data.table)
library(lme4)
library(geeM)
```

Set the working directory:

```{r, setup, include=FALSE}
data_loc <- "/Volumes/caas/CADRE CLC Data Project5/Clean Data/AK-SU-NETWORKS-ROUT/"
```

Read the datasets:

```{r, include=FALSE}

## environments
eda_env <- readRDS(paste0(data_loc, "eda_objects.rds"))

merged_network_participant_env <- 
  readRDS(paste0(data_loc, "merged_network_participant_objects.rds"))


## datasets
sns_dt_long_merged_ego_characteristics <- 
  merged_network_participant_env$sns_dt_long_merged_ego_characteristics

vacces_info_scores <- eda_env$vaccess_info_scores

full_dt <- eda_env$dt

## merging
sns_dt_long_merged_ego_characteristics <- merge(sns_dt_long_merged_ego_characteristics,
                                                   vacces_info_scores,
                                                    by = "MTURKID")
```

Query the dataset:

```{r}
head(colnames(full_dt), 10)
head(colnames(sns_dt_long_merged_ego_characteristics), 10)
```

## Vaccine acceptance reporting among the egos

Variable VA3: summary of whether one shot has been taken for 851 network contacts
Variable VA4: summary of whether vaccine was offered for 851 network contacts

```{r}
table(full_dt$FUVA3, exclude = NULL)
table(full_dt$FUVA4, exclude = NULL)

xtabs(~factor(FUVA3, exclude = NULL)+factor(FUVA4, exclude = NULL), 
      data = full_dt)

xtabs(~factor(FUVA3, exclude = NULL)+
        factor(FUSNCONSENT, exclude = NULL), 
      data = full_dt)

xtabs(~factor(FUVA4, exclude = NULL)+
        factor(FUSNCONSENT, exclude = NULL), 
      data = full_dt)

```

## Association of Vaccine Access among Egos with Alter Attitudes/Behaviors

```{r}
table(sns_dt_long_merged_ego_characteristics$va3, exclude = NULL)

table(sns_dt_long_merged_ego_characteristics$va4, exclude = NULL)

xtabs(~factor(va3, exclude = NULL)+factor(va4, exclude = NULL), 
      data = sns_dt_long_merged_ego_characteristics)

xtabs(~factor(va3, exclude = NULL)+factor(FUSNCONSENT, exclude = NULL), 
      data = sns_dt_long_merged_ego_characteristics)

xtabs(~factor(va4, exclude = NULL)+factor(FUSNCONSENT, exclude = NULL), 
      data = sns_dt_long_merged_ego_characteristics)

```



```{r}

```

### Test associations

```{r}
# Specify correlation structure
corstr <- "exchangeable"
```

VA3: Taken at least one dose of the vaccine

```{r}
sns_dt_long_merged_ego_characteristics$vh1_adequate <- 
  ifelse(sns_dt_long_merged_ego_characteristics$vh1 < 2, 1, 0)

model_vh1 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ 
                 SN27_reversed + SN28_reversed + SN29_reversed +
                   SN34_reversed + SN38_reversed,
                 #+ SN29 + SN33 + SN34 + SN37 + SN38, id = MTURKID, 
                 family="binomial", corstr = corstr)
summary(model_vh1)

model_vh1_sn27 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN27_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn27)

model_vh1_SN9 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN9,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN9)

model_vh1_SN28 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN28)

model_vh1_SN29 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN29_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN29)

# model_vh1_sn33 <- geem(data=sns_dt_long_merged_ego_characteristics, 
#                   vh1_adequate ~ SN33_reversed,
#                  family="binomial", corstr = corstr)
# summary(model_vh1)

model_vh1_SN34 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN28_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN28)

model_vh1_sn37 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN37_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_sn37)

model_vh1_SN38 <- geem(data=sns_dt_long_merged_ego_characteristics, 
                  vh1_adequate ~ SN38_reversed,
                 family="binomial", corstr = corstr)
summary(model_vh1_SN38)

#model_vh1_SN39 <- geem(data=sns_dt_long_merged_ego_characteristics, 
 #                 vh1_adequate ~ SN39_reversed,
  #               family="binomial", corstr = corstr)
#summary(model_vh1_SN39)
```

VH3: attitude towards receiving a COVID-19 

